\vspec{} and Friends: A suite of utilities to model spectroscopic phase curves of 3D exoplanet atmospheres in the presence of stellar variability.

### 2024-07-29 src/tex/ms.tex
Change the language about granulation parameters. I could not find any specific parameters in the Gordon paper, so I changed the wording to make it clear that these parameters were chosen arbitrarily.

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/granulation_lightcurve.pdf}
    \caption{
        Effect of granulation on the lightcurve of a star. This simulation assumes a mean
        10\% coverage by an inter-granule region whose temperature is 300K lower than the surrounding photosphere. It also assumes that the coverage value varies with a magnitude of 1\% on a timescale of 6 hours \TJ{find some constraints in Gordon paper}.
        }
    \script{granule_lc.py}
    \label{fig:gran_lc}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/granulation_lightcurve.pdf}
    \caption{
        Effect of granulation on the lightcurve of a star. The parameters chosen in this simulation mean that, on average, 10\% of the stellar surface is covered by the cool, inter-granule region with a temperature 300K lower than the surrounding photosphere, and that this coverage varies by about 1\% on a timescale of 6 hours.
        }
    \script{granule_lc.py}
    \label{fig:gran_lc}
\end{figure}
